A unified pseudo-$C_\ell$ framework

### 2018-07-30 doc/Paper/main.tex
link styles

\RequirePackage{docswitch}
% \flag is set by the user, through the makefile:
%    make note
%    make apj
% etc.
\setjournal{\flag}

\documentclass[\docopts]{\docclass}

% You could also define the document class directly
%\documentclass[]{emulateapj}

% Custom commands from LSST DESC, see texmf/styles/lsstdesc_macros.sty
\usepackage{lsstdesc_macros}

\usepackage{graphicx}
\graphicspath{{./}{./figures/}}
\bibliographystyle{apj}

% Add your own macros here:
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\lstset{ %
language=python,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=false,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)}          % if you want to add a comment within your code
}
\newcommand{\nv}{\hat{\bf n}}
\newcommand{\wtj}[6]{\left(\begin{array}{ccc} #1 & #2 & #3\\#4 & #5 & #6\end{array} \right)}
\newcommand{\todo}[1]{{\bf TODO: #1}}
\newcommand{\nmt}{{\tt NaMaster}}
\newcommand{\va}{{\mathbf{a}}}
\newcommand{\vb}{{\mathbf{b}}}
\newcommand{\mC}{{\sf C}}
\newcommand{\mM}{{\sf M}}

@@

% ======================================================================

@@

% Keywords are ignored in the LSST DESC Note style:
\dockeys{methods: data analysis -- methods: numerical}

@@

% ----------------------------------------------------------------------
% {% raw %}

@@

% ----------------------------------------------------------------------

@@

            \item {\sl Stars.} We add a second contaminant to $\delta_g$ associated with star contamination. For the full-sky realizations this contaminant is proportional to the fluctuation around the mean of a star density map generated using the LSST {\tt CatSim} catalog~\citet{2014SPIE.9150E..14C}. We modify this contaminant slightly by adding a white-noise component that dominates the small-scale spectrum beyond $\ell\simeq400$. We do this in order to simulate the noise-like distribution of stars on small scales as well as to include a contaminant source that, unlike dust, can surpass the signal on small scales. The amplitude of this contaminant is chosen such that its power spectrum is about 3\% of the signal at $\ell\sim400$.

@@

\bibliography{main}

@@

% Don't change these lines
\bsp	% typesetting comment

>>>>

\RequirePackage{docswitch}
\setjournal{\flag}

\documentclass[usenatbib]{mnrasb}

% Custom commands from LSST DESC, see texmf/styles/lsstdesc_macros.sty
\usepackage{lsstdesc_macros}
\usepackage{graphicx}

% Add your own macros here:
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{listings}
\lstset{ %
language=python,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=false,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)}          % if you want to add a comment within your code
}
%\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
\newcommand{\nv}{\hat{\bf n}}
\newcommand{\wtj}[6]{\left(\begin{array}{ccc} #1 & #2 & #3\\#4 & #5 & #6\end{array} \right)}
\newcommand{\todo}[1]{{\bf TODO: #1}}
\newcommand{\nmt}{{\tt NaMaster}}
\newcommand{\va}{{\mathbf{a}}}
\newcommand{\vb}{{\mathbf{b}}}
\newcommand{\mC}{{\sf C}}
\newcommand{\mM}{{\sf M}}

@@

@@

\dockeys{methods: data analysis -- methods: numerical}

@@

@@

@@

            \item {\sl Stars.} We add a second contaminant to $\delta_g$ associated with star contamination. For the full-sky realizations this contaminant is proportional to the fluctuation around the mean of a star density map generated using the LSST {\tt CatSim} catalog~\citep{2014SPIE.9150E..14C}. We modify this contaminant slightly by adding a white-noise component that dominates the small-scale spectrum beyond $\ell\simeq400$. We do this in order to simulate the noise-like distribution of stars on small scales as well as to include a contaminant source that, unlike dust, can surpass the signal on small scales. The amplitude of this contaminant is chosen such that its power spectrum is about 3\% of the signal at $\ell\sim400$.

@@

\bibliographystyle{mnrasb}
\bibliography{main}

@@

\bsp
